Prefetching SPARQL query cacher

### 2016-05-18 dissertation/cache-proxy.tex
redo refs

We have found it convenient to use classical inheritance in
combination with traits-based composition, but only when the base
class provide only fundamental functionality that is very likely to be
common to all implementations. For an example of this, see
Section~\ref{sec:cacher}.

@@

That new plan types can be integrated into the planner with ease, and
that the planner itself can be changed with very little effort is a
key contribution of the Attean system, which I have taken advantage of
in this work. That this is made easy is to the credit of traits, as
will become clear as we study the details of the implementation in
Section~\ref{sec:cacher}.

@@

\subsubsection{Query planner}

>>>>

We have found it convenient to use classical inheritance in
combination with traits-based composition, but only when the base
class provide only fundamental functionality that is very likely to be
common to all implementations. For an example of this, see
Section~\ref{sec:implqueryplan}.

@@

That new plan types can be integrated into the planner with ease, and
that the planner itself can be changed with very little effort is a
key contribution of the Attean system, which I have taken advantage of
in this work. That this is made easy is to the credit of traits, as
will become clear as we study the details of the implementation in
Section~\ref{sec:implqueryplan}.

@@

\subsubsection{Query planner}\label{sec:implqueryplan}
